### 2020-12-06 paper/localpsf.tex
edits to poiwwon weighting functions section

We choose the $i^\text{th}$ weighting function, $w_i(x)$, to be the solution to the following optimization problem:
\begin{equation}
\label{eq:wi_optimization_problem}
\begin{aligned}
\min_{w_i} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
\end{aligned}
\end{equation}
Here $\Delta$ is the Laplacian on $\Omega$ with pure Neumann boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness [cite Jacobsen], the weighting function $w_i$ is the ``flattest possible'' function (in a least-squares sense) that has Neumann boundary conditions and takes the value $1$ at point $x_i$, and zero at the points $x_j$, $j \neq i$. In Theorem \ref{thm:smoothest_interpolant}, we show that using these weighting functions yields the ``flattest possible'' interpolation of the convolution kernels $\varphi_i$, in a least-squares sense.

@@

Optimization problems \eqref{eq:wi_optimization_problem} and \eqref{eq:uy_optimization_problem} have unique continuous solutions when the spatial dimension is $1$, $2$, or $3$. When inverting for parameter fields defined on $4$ or higher spatial dimensions, the solution to this optimization problem does not exist, and Poisson interpolation (as described here) should not be used\footnote{The reason for this dependence on spatial dimension is related to the fact that the fundamental solution of the biharmonic equation is continuous in $3$ or less dimensions, but singular in $4$ or more dimensions. In the unusual scenario where one is inverting for a parameter field in $4$ or more spatial dimensions, one could use a modified Poisson interpolation where $\Delta$ is replaced with $\Delta^\alpha$ in the objective function of \eqref{eq:wi_optimization_problem}, where $\alpha>1$ is chosen so that the fundamental solution of $\Delta^{2\alpha}$ is continuous.}.

@@

\subsection{Computation of Poisson weighting functions}

In this section, we show how to efficiently solve optimization problem \eqref{eq:wi_optimization_problem}, and thus compute $w_i$. Briefly, constructing all $q$ of the functions $w_i$ requires solving the Poisson equation $2q$ times with different right hand side sources, and these Poisson PDE solves can be performed cheaply with multigrid. All the existing weighting functions, $\{w_i\}_{i=1}^q$, will change if a new point, $x_{q+1}$, is added. We present an efficient incremental algorithm for updating these weighting functions when a new point is added, in which we only need to perform two new Poisson PDE solves (rather than $2(q+1)$ new PDE solves).

>>>>

We choose the $i^\text{th}$ weighting function, $w_i(x)$, to be the solution to the following optimization problem:
\begin{equation}
\label{eq:wi_optimization_problem}
\begin{aligned}
\min_{w_i} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
\end{aligned}
\end{equation}
Here $\Delta$ is the Laplacian on $\Omega$ with pure Neumann boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness [cite Jacobsen], the weighting function $w_i$ is the ``flattest possible'' function (in a least-squares sense) that has Neumann boundary conditions and takes the value $1$ at point $x_i$, and zero at the points $x_j$, $j \neq i$. In Theorem \ref{thm:smoothest_interpolant}, we show that using these weighting functions yields the ``flattest possible'' interpolation of the convolution kernels $\varphi_i$, in a least-squares sense. Then in Section \ref{sec:computation_of_weighting_functions}, we show how to efficiently solve optimization problem \eqref{eq:wi_optimization_problem}, and thus compute $w_i$. Constructing all $q$ of the functions $w_i$ requires solving the Poisson equation $2q$ times with different right hand side sources, and these Poisson PDE solves can be performed cheaply with multigrid. All the existing weighting functions, $\{w_i\}_{i=1}^q$, will change if a new point, $x_{q+1}$, is added. However, we present an efficient incremental algorithm for updating these weighting functions when a new point is added, so that we only need to perform two new Poisson PDE solves, rather than $2(q+1)$ new PDE solves.

It is important to note that optimization problems \eqref{eq:wi_optimization_problem} only has a unique continuous solution when the spatial dimension is $1$, $2$, or $3$. When inverting for parameter fields defined on $4$ or higher spatial dimensions, the solution to this optimization problem does not exist, and these weighting functions should not be used\footnote{The reason for this dependence on spatial dimension is related to the fact that the fundamental solution of the biharmonic equation is continuous in $3$ or less dimensions, but singular in $4$ or more dimensions. In the unusual scenario where one is inverting for a parameter field in $4$ or more spatial dimensions, one could use a modified Poisson interpolation where $\Delta$ is replaced with $\Delta^\alpha$ in the objective function of \eqref{eq:wi_optimization_problem}, where $\alpha>1$ is chosen so that the fundamental solution of $\Delta^{2\alpha}$ is continuous.}.

@@

@@

\subsection{Computation of Poisson weighting functions}
\label{sec:computation_of_weighting_functions}
